Hydras \& Co.

### 2022-10-28 doc/chapter-fol.tex
fix a latex error
fix a snippet error
Minor changes in Latex files

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.MoreAck.fol_Examples.html}{MoreAck.fol\_Examples}

\inputsnippets{fol_Examples/instantiations}

@@

\inputsnippets{fol_Examples/v1Plus01}

@@

\label{fol:examplesf1f2f3}
\begin{enumerate}
\item $\forall\,v_0, v_0=0 \vee \exists\;v_1,\, v_0= S\;v_1$
\item $\exists\,v_2,\, 0< v_2 \wedge 4=v_2+v_2$
\item $ v_0=0 \vee \exists\;v_1,\, v_0= S\;v_1$
\item $v_0= v_1 + v_1 \leftrightarrow v_0 = v_1 \times 2$
\end{enumerate}
\inputsnippets{fol_Examples/f1Example}
\inputsnippets{fol_Examples/f2Example}

@@

\inputsnippets{fol/depthDef, fol_Examples/depthCompute}

@@

\inputsnippets{fol/ltDepth, fol_Examples/ltdepth1}

@@

\inputsnippets{fol_examples/depthRecDemo}

@@

>>>>

@@

@@

\label{fol:examplesf1f2f3}
\begin{enumerate}
\item $\forall\,v_0, v_0=0 \vee \exists\;v_1,\, v_0= S\;v_1$
\item $\exists\,v_2,\, 0< v_2 \wedge 4=v_2+v_2$
\item $ v_0=0 \vee \exists\;v_1,\, v_0= S\;v_1$
\item $v_0= v_1 + v_1 \leftrightarrow v_0 = v_1 \times 2$
\end{enumerate}
\inputsnippets{fol_Examples/f1Example}

@@

\inputsnippets{fol/depthDef,  fol_Examples/DepthCompute}

@@

\inputsnippets{fol_Examples/ltDepth1}

@@

\inputsnippets{fol_Examples/depthRecDemo}

@@

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.Ackermann.LNN.html}{Ackermann.LNN\_Examples}

\inputsnippets{LNN/instantiations}
